# Electricity profiles

This chapter provides electricity profiles and a R coding technique. 
Electricity profiles are illustrated to give an insight into profile behavior. 
R coding technique are given in order to understand the process flow and 
manage the big data obtained from several sources in the organization.


## Electricity generation profiles for EGAT sale

Before the project starts, library are required as follows:

```{r, library setting, results='hide', message=FALSE}
library(tidyverse) #For data manipulation
library(readxl) #For reading the excel sheet
library(scales)
library(glue)
library(knitr)
```

Design a theme and lines for figures
```{r, create theme , warning=FALSE}
#----- Create general theme for figures -----####
ThemeLine <- 
  theme_bw() +
  theme(
    panel.border=element_rect(fill=NA),
    panel.grid.minor = element_line(color = NA), 
    #    axis.title=element_text(size=5),
    #    axis.text.x = element_text(hjust=1,size = 10, angle = 0),
    axis.line=element_line(colour="black"),
    panel.background=element_rect(fill = "white"),
    panel.grid.major.x=element_line(linetype="dashed",colour="grey",size=0.5),
    panel.grid.major.y = element_blank(),
    # panel.grid.major=element_blank(),
    strip.background=element_rect(fill="white", colour="white"),
    strip.text.x = element_text(size=10, colour = "black", angle = 0,face="bold"),
    axis.text.x=element_text(size = 10,angle=45, vjust=0.9, hjust=1, margin = unit(c(t = 0.3, r = 0, b = 0, l = 0), "cm")),
    axis.text.y=element_text(size = 10,margin = unit(c(t = 0, r = 0.3, b = 0, l = 0), "cm")),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10),
    axis.ticks.length=unit(-0.15,"cm")
  )
```

Create line palettes for drawing figures
```{r, assign line color, message=FALSE}
linepalette1 <- c("#4DAF4A","#FF7F00","#377EB8","#E41A1C","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#B3DE69","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")
linepalette2 <- c("#E41A1C","#FF7F00","#377EB8","#B3DE69","#4DAF4A","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")

```

Create lists to store profile data, profile figure, and summary data.
```{r, making list to store data, echo=TRUE}

profiledata <- list()
profilefigure <- list()
summarydata <- list()
```

Create a varaible to assign the output directory of figures
```{r, making variable for out directiry, echo=TRUE}
#----- Make variable for output directory -----####
outfigdir <- c("figures/")
```

The 2019 MEA EGAT sale profile data is extracted from the excel file provided by the "National Load Forecast Section"

```{r, extract MEA EGAT sale from excel, echo=TRUE}
#----- ____ -----####

#----- The 2019 MEA EGAT sale profile ----####
# Profile data ####
profile <- 
  read_excel("./raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
           sheet = "Load Curve",
           range = "C3:D17523"
            ) %>% 
  select(datetime = `Date/Time`, MEA) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, MEA)
```


Get a peak and a minimum demands in MW by creating `maxv` and `minv` variables.
The electricity sale (in EGAT case we call "Energy") to MEA by EGAT is calculated. 
The equation is as followed: 
```{r, calculate values, echo=TRUE}
# Summary data ####
maxv <- ceiling(max(profile$MEA)) # Get a peak MW
minv <- floor(min(profile$MEA)) # Get a min MW
energy <- sum(profile$MEA)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
            group_by(year) %>% 
            filter(MEA == max(MEA)) %>% 
            pull(datetime)
min_day <- profile %>% #Find a peak day
           group_by(year) %>% 
           filter(MEA == min(MEA)) %>% 
           pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r, MEA EGAT sale profile, echo=TRUE}
# Plot a profile ####
 
profile_plot <-
    ggplot() + 
    geom_line(data=profile, 
              aes(x = datetime, 
                  y = MEA,
                  group = month,
                  color = as.factor(month)),
              show.legend = FALSE) +
    ThemeLine +
    labs(x = NULL,
         y = "EGAT sale to MEA (MW)")+
    scale_x_datetime(breaks=date_breaks("1 month"), 
                     labels=date_format("%b %y")) +
    scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                       limits = c(0, round(maxv, -3))) +  
    scale_color_manual(values = linepalette1) +
    geom_point(data=summary,
               aes(x = peak_day, y = peak_mw))+
    geom_text(data = summary,
              aes(x = peak_day, y = round(maxv, -3)),
              label = glue("Peak {maxv} MW \n@ {peak_day}"))+
    geom_point(data=summary,
               aes(x = min_day, y = min_mw))+
    geom_text(data = summary,
              aes(x = min_day, y = round(minv, -3)),
              label = glue("Minimum {minv} MW \n@ {min_day}"),
              hjust = 0,
              vjust = 1.5)
```

The EGAT sale to MEA 
```{r, plot MEA EGAT sale, echo=FALSE, fig.cap = 'EGAT sale to MEA in 2019',fig.width=10, fig.height=5, fig.align='center'}
profile_plot
```

