# Getting started with R

The R language is used in this project. It is applied to analyze and visualize the electricity generation, electricity demand, electricity profiles. Therefore, R language is needed to install
in your computer. R can be run on several operating system.

* Installing R on [Windows](https://cran.r-project.org/bin/windows/)
* Installing R on [macOS](https://cran.r-project.org/bin/macosx/)

There is an integrated development environment (IDE) for R language. The IDE is an excellent text editor with syntax highlight and project viewer. The Rstudio IDE can be downloaded [here](https://posit.co/downloads/).



## Project initial settings
### Installing packages

Required packages can be downloaded by using the command `install.packages()`. A R code chunk is given below.

```{r, installing packages, echo=TRUE, warning=FALSE, message=FALSE}
install.packages("tidyverse", "readxl","scales", "glue","knitr")
```


### Packages settings
Before the project starts, packages are required as follows:

* A `tidyverse` package is a bunch of packages to handle with a data analysis (for more information click [here](https://www.tidyverse.org/packages/)). It consists of data manipulation and visualization as follows:
  * A `ggplot2` [package](https://ggplot2.tidyverse.org/) is for data visualization.
  * A `dplyr` [package](https://dplyr.tidyverse.org/) is for data manipulation.
  * A `tidyr` [package](https://tidyr.tidyverse.org/) is for data tidying.
  * A `readr` [package](https://readr.tidyverse.org/) is for data import.
  * A `purrr` [package](https://purrr.tidyverse.org/) is for functional programming.
  * A `tibble` [package](https://tibble.tidyverse.org/) is a modern reimagining of the data.frame.
  * A `stringr` [package](https://github.com/tidyverse/stringr) is for strings.
  * A `forcats` [package](https://github.com/tidyverse/forcats) is for factors.
  * A `lubridate` [package](https://github.com/tidyverse/lubridate) is for date and time.
* A `readxl` [package](https://readxl.tidyverse.org/) is used for read data from **Excel** into R.
* A `scales` [package](https://scales.r-lib.org/) is applied to scale plots in the ggplot2 package.
* A `glue` [package](https://glue.tidyverse.org/) interprets strings literal. The package embeds R expressions and inserts into argument string.
* A `knitr` [package](https://github.com/yihui/knitr) is a lightweight API's designed to give users full control of the output without heavy coding work. In this project, the package is used for making a HTML. 


```{r, library setting, results='hide', message=FALSE}
library(tidyverse) #For data manipulation
library(readxl) #For reading the excel sheet
library(scales)
library(glue)
library(knitr)
library(plotly)
```

### Theme settings
Theme and lines for figures are set in a variable named `Themeline` as follows:

* `theme_bw()` [function](https://ggplot2.tidyverse.org/reference/ggtheme.html) provides a black and white theme.
* `theme()` function applied for setting theme and line represented in plots.
* `linepalette1` and `linepalette1` variables set line colors.

```{r, theme setting, results='hide', message=FALSE, warning=FALSE}
ThemeLine <- 
  theme_bw() +
  theme(
    panel.border=element_rect(fill=NA),
    panel.grid.minor = element_line(color = NA), 
    #    axis.title=element_text(size=5),
    #    axis.text.x = element_text(hjust=1,size = 10, angle = 0),
    axis.line=element_line(colour="black"),
    panel.background=element_rect(fill = "white"),
    panel.grid.major.x=element_line(linetype="dashed",colour="grey",linewidth = 0.5),
    panel.grid.major.y = element_blank(),
    # panel.grid.major=element_blank(),
    strip.background=element_rect(fill="white", colour="white"),
    strip.text.x = element_text(size=10, colour = "black", angle = 0,face="bold"),
    axis.text.x=element_text(size = 10,angle=45, vjust=0.9, hjust=1, margin = unit(c(t = 0.3, r = 0, b = 0, l = 0), "cm")),
    axis.text.y=element_text(size = 10,margin = unit(c(t = 0, r = 0.3, b = 0, l = 0), "cm")),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10),
    axis.ticks.length=unit(-0.15,"cm")
  )
linepalette1 <- c("#4DAF4A","#FF7F00","#377EB8","#E41A1C","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#B3DE69","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")
linepalette2 <- c("#E41A1C","#FF7F00","#377EB8","#B3DE69","#4DAF4A","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")

```
### Directory setting
Lists are create to store variables.

```{r, make list}
#----- Make a list of profile to store data -----####

profiledata <- list()
profilefigure <- list()
summarydata <- list()
```

```{r, variable for output}
#----- Make variable for output directory -----####
outfigdir <- c("figures/")
```