# Electricity profiles 
This chapter provides electricity profiles and a R coding technique. 
Electricity profiles are illustrated to give an insight into profile behavior. 
R coding technique are given in order to understand the process flow and 
manage the big data obtained from several sources in the organization.

## Initial settings
### Packages setting
Before the project starts, packages are required as follows:

* A `tidyverse` package is a bunch of packages to handle with a data analysis (for more information click [here](https://www.tidyverse.org/packages/)). It consists of data manipulation and visualization as follows:
  * A `ggplot2` [package](https://ggplot2.tidyverse.org/) is for data visualization.
  * A `dplyr` [package](https://dplyr.tidyverse.org/) is for data manipulation.
  * A `tidyr` [package](https://tidyr.tidyverse.org/) is for data tidying.
  * A `readr` [package](https://readr.tidyverse.org/) is for data import.
  * A `purrr` [package](https://purrr.tidyverse.org/) is for functional programming.
  * A `tibble` [package](https://tibble.tidyverse.org/) is a modern reimagining of the data.frame.
  * A `stringr` [package](https://github.com/tidyverse/stringr) is for strings.
  * A `forcats` [package](https://github.com/tidyverse/forcats) is for factors.
  * A `lubridate` [package](https://github.com/tidyverse/lubridate) is for date and time.
* A `readxl` [package](https://readxl.tidyverse.org/) is used for read data from **Excel** into R.
* A `scales` [package](https://scales.r-lib.org/) is applied to scale plots in the ggplot2 package.
* A `glue` [package](https://glue.tidyverse.org/) interprets strings literal. The package embeds R expressions and inserts into argument string.
* A `knitr` [package](https://github.com/yihui/knitr) is a lightweight API's designed to give users full control of the output without heavy coding work. In this project, the package is used for making a HTML. 

```{r, library setting, results='hide', message=FALSE}
library(tidyverse) #For data manipulation
library(readxl) #For reading the excel sheet
library(scales)
library(glue)
library(knitr)
library(plotly)
```
### Theme setting
Theme and lines for figures are set in a variable named `Themeline` as follows:

* `theme_bw()` [function](https://ggplot2.tidyverse.org/reference/ggtheme.html) provides a black and white theme.
* `theme()` function applied for setting theme and line represented in plots.
* `linepalette1` and `linepalette1` variables set line colors.

```{r, theme setting, results='hide', message=FALSE, warning=FALSE}
ThemeLine <- 
  theme_bw() +
  theme(
    panel.border=element_rect(fill=NA),
    panel.grid.minor = element_line(color = NA), 
    #    axis.title=element_text(size=5),
    #    axis.text.x = element_text(hjust=1,size = 10, angle = 0),
    axis.line=element_line(colour="black"),
    panel.background=element_rect(fill = "white"),
    panel.grid.major.x=element_line(linetype="dashed",colour="grey",linewidth = 0.5),
    panel.grid.major.y = element_blank(),
    # panel.grid.major=element_blank(),
    strip.background=element_rect(fill="white", colour="white"),
    strip.text.x = element_text(size=10, colour = "black", angle = 0,face="bold"),
    axis.text.x=element_text(size = 10,angle=45, vjust=0.9, hjust=1, margin = unit(c(t = 0.3, r = 0, b = 0, l = 0), "cm")),
    axis.text.y=element_text(size = 10,margin = unit(c(t = 0, r = 0.3, b = 0, l = 0), "cm")),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10),
    axis.ticks.length=unit(-0.15,"cm")
  )
linepalette1 <- c("#4DAF4A","#FF7F00","#377EB8","#E41A1C","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#B3DE69","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")
linepalette2 <- c("#E41A1C","#FF7F00","#377EB8","#B3DE69","#4DAF4A","#984EA3","#F781BF","#8DD3C7","#FB8072","#80B1D3","#FDB462","#FCCDE5","#D9D9D9","#BC80BD","#CCEBC5","#FFED6F","#7f878f","#A65628","#FFFF33")

```
### Directory setting
Lists are create to store variables.

```{r, make list}
#----- Make a list of profile to store data -----####

profiledata <- list()
profilefigure <- list()
summarydata <- list()
```

```{r, variable for output}
#----- Make variable for output directory -----####
outfigdir <- c("figures/")
```
## The EGAT electrity sale profiles

### The 2019 Metropolitan Electricity Authority (MEA) EGAT sale profile
The electricity sale profile from EGAT is given by the Power System Control and Operation Division (ฝ่ายควบคุมระบบกำลังไฟฟ้า).


```{r, MEA EGAT sale}
#----- The 2019 MEA EGAT sale profile ----####
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
           sheet = "Load Curve",
           range = "C3:D17523"
            ) %>% 
  select(datetime = `Date/Time`, MEA) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, MEA)
```

```{r profile-egat-to-mea-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to MEA profile',
  booktabs = TRUE
)
```

The peak, minimun in the unit of MW, and an electricity sale to MEA in GWh from the profile are calculated.
The electricity sale to MEA (in GWh) is calculated by the summation of profile in MW divided by 2000.

The reason to divide by **2,000** is that the profile is given a time stamp in **every 30-min**. There are **17,520** values. Therefore, the profile is divided by **2** to get the results in **every 1 hr.**. We divided the output by **1,000** to convert the unit **from MWh to GWh** (see equation \@ref(eq:energycal)).

\begin{equation}
 Ene_{t}=\frac{\sum_{h=1}^{17520} (Prf_{t,h})}{2*1000}
 (\#eq:energycal)
\end{equation} 

Where, $Ene_{t}$ denotes an calculated energy (electricity) in year $t$.\
$Prf_{t,h}$ denotes a profile ($Prf$) in the unit of MW in year $t$ at a time stamp $h$.\
$h$ denotes a time stamp in a 30-minute interval. Therefore, there are **17,520 intervals** in a year (8,760 hrs.).

```{r, find peak and min MW}
# Summary data ####
maxv <- ceiling(max(profile$MEA)) # Get a peak MW
minv <- floor(min(profile$MEA)) # Get a min MW
energy <- sum(profile$MEA)/2000 # Calculate the energy
```

The peak and minimum MW days are also needed to assess in order to provide the maximum and minimum a saled electricity from EGAT to MEA.
```{r, peak & min day}
peak_day <- profile %>% #Find a peak day
            group_by(year) %>% 
            filter(MEA == max(MEA)) %>% 
            pull(datetime)
min_day <- profile %>% #Find a peak day
           group_by(year) %>% 
           filter(MEA == min(MEA)) %>% 
           pull(datetime)
```

Load factor is calculated by the energy in equation \@ref(eq:energycal) divided a maximum energy. A maximum energy is **the peak multiplied by 8760 hours**. Result is presented in a percentage.

\begin{equation}
 LF_{t}=\frac{Energy_{t}}{Peak_{d,h} * 8760}*100 
 (\#eq:loadfactorcal)
\end{equation} 

Where, $LF_{t}$ denotes the load factor at year $t$ in percentage.\
$Energy_{t}$ denotes the calculated energy from equation \@ref(eq:energycal) at year $t$ in GWh.\
$Peak_{d,h}$ denotes the peak electricity sale on the date $d$ at time $h$.


```{r, load factor}
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
```

Create a table to store relevant data.
```{r, summary data}
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```
In 2019, the electricity sale to MEA by EGAT reached it peak **`r format(maxv, scientific=FALSE, big.mark = ",")`** MW on **`r peak_day`**. The energy (electricity) sale to MEA was **`r format(energy, scientific=FALSE, big.mark = ",")`** GWh.
The summary of the electricity sale to MEA by EGAT in 2019 is given in Table \@ref(tab:sum-egat-to-mea-2019).

```{r sum-egat-to-mea-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to MEA in 2019',
  booktabs = TRUE
)
```


The 2019 electricity sale profile from EGAT to MEA is illustrated (see Figure \@ref(fig:EGAT-sale-to-MEA-2019)).
```{r, EGAT sale to MEA in 2019}
profile_plot <-
    ggplot() + 
    geom_line(data=profile, 
              aes(x = datetime, 
                  y = MEA,
                  group = month,
                  color = as.factor(month)),
              show.legend = FALSE) +
    ThemeLine +
    labs(x = NULL,
         y = "EGAT sale to MEA (MW)")+
    scale_x_datetime(breaks=date_breaks("1 month"), 
                     labels=date_format("%b %y")) +
    scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                       limits = c(0, round(maxv, -3))) +  
    scale_color_manual(values = linepalette1) +
    geom_point(data=summary,
               aes(x = peak_day, y = peak_mw))+
    geom_text(data = summary,
              aes(x = peak_day, y = round(maxv, -3)),
              label = glue("Peak {maxv} MW \n@ {peak_day}"))+
    geom_point(data=summary,
               aes(x = min_day, y = min_mw))+
    geom_text(data = summary,
              aes(x = min_day, y = round(minv, -3)),
              label = glue("Minimum {minv} MW \n@ {min_day}"),
              hjust = 0,
              vjust = 1.5)
```


```{r, EGAT-sale-to-MEA-2019, echo=FALSE, fig.cap='EGAT electricity sale profile to MEA in 2019.', fig.align='center', out.width= '90%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

Outputs are saved. Outputs are listed as follows:

* Create a file name `mea_egtsle_2019.png`
* Save a plot in a directory using `ggsave()` [function](https://ggplot2.tidyverse.org/reference/ggsave.html)
* Save profile data in a `profiledata` list
* Save figures in a `profilefigure` list
* Save summary data in a `summarydata` list
```{r, save output}

outputfigure <- paste0(outfigdir, "mea_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("mea_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("mea_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_mea_egtsle_2019" = summary))
```

### The 2019 Provincial Electricity Authority (PEA) EGAT sale profiles {#peaegtsle2019}
#### The 2019 PEA-R1 (Central region) EGAT sale profile
Read a profile data
```{r, profile_PEA-R1_egtsle2019, echo=TRUE}
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:E17523"
  ) %>% 
  select(datetime = `Date/Time`, PEA_R1) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, PEA_R1)
```

```{r profile-egat-to-pea-r1-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R1 profile',
  booktabs = TRUE
)
```


```{r, summary_PEA-R1_egtsle2019}
maxv <- ceiling(max(profile$PEA_R1)) # Get a peak MW
minv <- floor(min(profile$PEA_R1)) # Get a min MW
energy <- sum(profile$PEA_R1)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R1 == max(PEA_R1)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R1 == min(PEA_R1)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) 
```

```{r sum-egat-to-PEA-R1-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R1 in 2019',
  booktabs = TRUE
)
```

The 2019 electricity sale profile from EGAT to PEA-R1 is illustrated (see Figure \@ref(fig:EGAT-sale-to-PEA-R1-2019)).

```{r,plot_PEA-R1_egtsle2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = PEA_R1,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R1 (Central region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                     limits = c(0, round(maxv, -3))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 1.5)
```

```{r,EGAT-sale-to-PEA-R1-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA-R1 in 2019.', fig.align='center', out.width= '90%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

```{r, sv_PEA-R1_egtsle2019}
outputfigure <- paste0(outfigdir, "pea_r1_central_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("pea_r1_central_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("pea_r1_central_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_pea_r1_central_egtsle_2019" = summary))
```

#### The 2019 PEA-R2 (North Eastern region) EGAT sale profile


```{r, profile_PEA-R2_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:F17523"
  ) %>% 
  select(datetime = `Date/Time`, PEA_R2) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, PEA_R2) #%>% 
# mutate(strdatetime = as.factor(strptime(glue("{year}-{month}-{day} {time}"), "%Y-%m-%d %H:%M:%S")))
```

```{r profile-egat-to-PEA-R2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R2 profile',
  booktabs = TRUE
)
```

```{r, summary_PEA-R2_egtsle2019}
# Summary data ####
maxv <- ceiling(max(profile$PEA_R2)) # Get a peak MW
minv <- floor(min(profile$PEA_R2)) # Get a min MW
energy <- sum(profile$PEA_R2)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R2 == max(PEA_R2)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R2 == min(PEA_R2)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r sum-egat-to-PEA-R2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R2 in 2019',
  booktabs = TRUE
)
```


```{r, plot_PEA-R2_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = PEA_R2,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R2 (North Eastern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                     limits = c(0, round(maxv, -3))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 1.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "pea_r2_northeastern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("pea_r2_northeastern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("pea_r2_northeastern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_pea_r2_northeastern_egtsle_2019" = summary))
```

The 2019 electricity sale profile from EGAT to PEA-R2 is illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R2-2019)).

```{r,EGAT-sale-to-PEA-R2-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA-R2 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 PEA-R3 (Southern region) EGAT sale profile

```{r, profile_PEA-R3_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:G17523"
  ) %>% 
  select(datetime = `Date/Time`, PEA_R3) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, PEA_R3) #%>% 
# mutate(strdatetime = as.factor(strptime(glue("{year}-{month}-{day} {time}"), "%Y-%m-%d %H:%M:%S")))
```

```{r profile-egat-to-PEA-R3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R3 profile',
  booktabs = TRUE
)
```

```{r, summary_PEA-R3_egtsle2019}

# Summary data ####
maxv <- ceiling(max(profile$PEA_R3)) # Get a peak MW
minv <- floor(min(profile$PEA_R3)) # Get a min MW
energy <- sum(profile$PEA_R3)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R3 == max(PEA_R3)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R3 == min(PEA_R3)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r sum-egat-to-PEA-R3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R3 in 2019',
  booktabs = TRUE
)
```

```{r, plot_PEA-R3_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = PEA_R3,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R3 (Southern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                     limits = c(0, round(maxv, -3))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 1.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "pea_r3_southern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("pea_r3_southern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("pea_r3_southern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_pea_r3_southern_egtsle_2019" = summary))
```

The 2019 electricity sale profile from EGAT to PEA-R3 is illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R3-2019)).

```{r,EGAT-sale-to-PEA-R3-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA-R3 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 PEA-R4 (Northern region) EGAT sale profile

```{r, profile_PEA-R4_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:H17523"
  ) %>% 
  select(datetime = `Date/Time`, PEA_R4) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, PEA_R4) #%>% 

```

```{r profile-egat-to-PEA-R4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R4 profile',
  booktabs = TRUE
)
```

```{r summary_PEA-R4_egtsle2019, echo=FALSE, tidy=FALSE }
# Summary data ####
maxv <- ceiling(max(profile$PEA_R4)) # Get a peak MW
minv <- floor(min(profile$PEA_R4)) # Get a min MW
energy <- sum(profile$PEA_R4)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R4 == max(PEA_R4)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA_R4 == min(PEA_R4)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-PEA-R4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R4 in 2019',
  booktabs = TRUE
)
```

```{r, plot_PEA-R4_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = PEA_R4,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R4 (Northern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.2,1000),
                     limits = c(0, round(maxv, -3)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0.5,
            vjust = 1.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "pea_r4_northern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("pea_r4_northern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("pea_r4_northern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_pea_r4_northern_egtsle_2019" = summary))
```

The 2019 electricity sale profile from EGAT to PEA-R4 is illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R4-2019)).

```{r,EGAT-sale-to-PEA-R4-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA-R4 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 PEA (All regions) EGAT sale profile

```{r profile_PEA_allregion_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:I17523"
  ) %>% 
  select(datetime = `Date/Time`, PEA) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, PEA) 
```

```{r profile-egat-to-PEA-allregion-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA (all regions) profile',
  booktabs = TRUE
)
```

```{r summary_PEA-allreion_egtsle2019, echo=FALSE, tidy=FALSE }
# Summary data ####
maxv <- ceiling(max(profile$PEA)) # Get a peak MW
minv <- floor(min(profile$PEA)) # Get a min MW
energy <- sum(profile$PEA)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA == max(PEA)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(PEA == min(PEA)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-PEA-allregion-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA (all regions) in 2019',
  booktabs = TRUE
)
```

```{r plot_PEA-allregion_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = PEA,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA (All regions) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,1000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "pea_allregion_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("pea_allregion_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("pea_allregion_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_pea_allregion_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to PEA (all regions) is illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-allregion-2019)).

```{r,EGAT-sale-to-PEA-allregion-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA (all regions) in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 Direct Customer (DC) EGAT sale profiles {#dcegtsle2019}
#### The 2019 DC in in PEA R1 (Central region) EGAT sale profiles

```{r profile_dcr1_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:J17523"
  ) %>% 
  select(datetime = `Date/Time`, DCs_R1) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, DCs_R1) #%>% 

```

```{r profile-egat-to-dcr1-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to direct customer in PEA-R1 profile',
  booktabs = TRUE
)
```


```{r summary_dcr1_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$DCs_R1)) # Get a peak MW
minv <- floor(min(profile$DCs_R1)) # Get a min MW
energy <- sum(profile$DCs_R1)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs_R1 == max(DCs_R1)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs_R1 == min(DCs_R1)) %>% 
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-dcr1-2019, echo=TRUE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to direct customer in PEA-R1 in 2019',
  booktabs = TRUE
)
```

```{r plot_dcr1_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = DCs_R1,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to direct customers in PEA R1 (Central region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,100),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -2)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 1.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "dc_r1_central_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("dc_r1_central_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("dc_r1_central_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_dc_r1_central_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to direct customer in PEA-R1 is illustrated in Figure \@ref(fig:EGAT-sale-to-DCR1-2019)).

```{r,EGAT-sale-to-DCR1-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to direct customer in PEA-R1 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 DC in in PEA R2 (North Eastern region) EGAT sale profiles

```{r profile_dcr2_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:K17523"
  ) %>% 
  select(datetime = `Date/Time`, DCs_R2) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, DCs_R2) #%>% 

```

```{r profile-egat-to-dcr2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to direct customer in PEA-R2 profile',
  booktabs = TRUE
)
```

```{r summary_dcr2_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$DCs_R2)) # Get a peak MW
minv <- floor(min(profile$DCs_R2)) # Get a min MW
energy <- sum(profile$DCs_R2)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs_R2 == max(DCs_R2)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(DCs_R2 == min(DCs_R2)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-dcr2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to direct customer in PEA-R2 in 2019',
  booktabs = TRUE
)
```

```{r plot_dcr2_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = DCs_R2,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to direct customers in PEA R2 (North Eastern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,100),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -2)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "dc_r2_northeastern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("dc_r2_northeastern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("dc_r2_northeastern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_dc_r2_northeastern_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to direct customer in PEA-R2 is illustrated in Figure \@ref(fig:EGAT-sale-to-DCR2-2019)).

```{r,EGAT-sale-to-DCR2-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to direct customer in PEA-R2 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 DC in in PEA R3 (Southern region) EGAT sale profiles

```{r profile_dcr3_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:L17523"
  ) %>% 
  select(datetime = `Date/Time`, DCs_R3) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, DCs_R3) #%>% 

```

```{r profile-egat-to-dcr3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to direct customer in PEA-R3 profile',
  booktabs = TRUE
)
```

```{r summary_dcr3_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$DCs_R3)) # Get a peak MW
minv <- floor(min(profile$DCs_R3)) # Get a min MW
energy <- sum(profile$DCs_R3)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs_R3 == max(DCs_R3)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(DCs_R3 == min(DCs_R3)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-dcr3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to direct customer in PEA-R3 in 2019',
  booktabs = TRUE
)
```

```{r plot_dcr3_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = DCs_R3,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to direct customers in PEA R3 (Southern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2),100),
                     limits = c(0, round(maxv, -2))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"))+
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -2)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "dc_r3_southern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("dc_r3_southern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("dc_r3_southern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_dc_r3_southern_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to direct customer in PEA-R3 is illustrated in Figure \@ref(fig:EGAT-sale-to-DCR3-2019)).

```{r,EGAT-sale-to-DCR3-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to direct customer in PEA-R3 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 DC in in PEA R4 (Northern region) EGAT sale profiles

```{r profile_dcr4_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:M17523"
  ) %>% 
  select(datetime = `Date/Time`, DCs_R4) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, DCs_R4) #%>% 

```

```{r profile-egat-to-dcr4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to direct customer in PEA-R4 profile',
  booktabs = TRUE
)
```

```{r summary_dcr4_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$DCs_R4)) # Get a peak MW
minv <- floor(min(profile$DCs_R4)) # Get a min MW
energy <- sum(profile$DCs_R4)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs_R4 == max(DCs_R4)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(DCs_R4 == min(DCs_R4)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-dcr4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to direct customer in PEA-R4 in 2019',
  booktabs = TRUE
)
```

```{r plot_dcr4_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = DCs_R4,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to direct customers in PEA R4 (Northern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-1),10),
                     limits = c(0, round(maxv, -1))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -1)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -1)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = -0.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "dc_r4_northern_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("dc_r4_northern_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("dc_r4_northern_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("dc_r4_northern_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to direct customer in PEA-R4 is illustrated in Figure \@ref(fig:EGAT-sale-to-DCR4-2019)).

```{r,EGAT-sale-to-DCR4-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to direct customer in PEA-R4 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

#### The 2019 DC in in PEA (All regions) EGAT sale profiles

```{r profile_dcallregions_egtsle2019}
# Profile data ####
profile <- 
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "C3:N17523"
  ) %>% 
  select(datetime = `Date/Time`, DCs) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, DCs) #%>% 
```

```{r profile-egat-to-dcallregions-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to direct customer in PEA (all regions) profile',
  booktabs = TRUE
)
```

```{r summary_dcallregion_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$DCs)) # Get a peak MW
minv <- floor(min(profile$DCs)) # Get a min MW
energy <- sum(profile$DCs)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(DCs == max(DCs)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(DCs == min(DCs)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r sum-egat-to-dcallregions-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to direct customer in PEA (all regions) in 2019',
  booktabs = TRUE
)
```

```{r plot_dcallregions_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = DCs,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to direct customers in PEA (All regions) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,100),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5,
            vjust = 1.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -2)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            # hjust = 0,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "dc_allregions_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("dc_allregions_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("dc_allregions_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_dc_allregions_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to direct customer in PEA (all regions) is illustrated in Figure \@ref(fig:EGAT-sale-to-DCALLREG-2019)).

```{r,EGAT-sale-to-DCALLREG-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to direct customer in PEA (all regions) in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 PEA R1 & DC R1 (Central region) EGAT electrity sale profiles

The electricity profile in PEA region is combined the electricity profile in PEA regions (see section \@ref(peaegtsle2019)) and DC in PEA regions (see section \@ref(dcegtsle2019))

\begin{equation}
 Prf_{r,t,h}=\ Prf_{PEA,t,h} + Prf_{DC,t,h}
 (\#eq:prfPeaDcCal)
\end{equation} 

Where, $Prf_{r,t,h}$ denotes an calculated profile in region $r$, year $t$, and time $h$ (MW).\
$Prf_{PEA,t,h}$ denotes a profile in $PEA$ from each region in year $t$ at time $h$ (MW).\
$Prf_{DC,t,h}$ denotes a profile from direct customer ($DC$) in each PEA region in year $t$ at time $h$ (MW).

```{r profile_pear1&dcr1_egtsle2019}
# Profile data ####
profile <- 
  
  profiledata$pea_r1_central_egtsle_2019%>%
  mutate(dc_r1 = profiledata$dc_r1_central_egtsle_2019$DCs_R1,
         r1_egt_sle = PEA_R1 + dc_r1) %>% 
  select(-PEA_R1, -dc_r1)

```

```{r, profile-egat-to-pear1-dcr1-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R1 and direct customer in PEA R1 profile',
  booktabs = TRUE
)
```

```{r summary_pear1&dcr1_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$r1_egt_sle)) # Get a peak MW
minv <- floor(min(profile$r1_egt_sle)) # Get a min MW
energy <- sum(profile$r1_egt_sle)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r1_egt_sle == max(r1_egt_sle)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r1_egt_sle == min(r1_egt_sle)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egat-to-pear1-dcr1-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R1 and direct customer in PEA R1 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear1&dcr1_egtsle2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r1_egt_sle,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R1 & direct customers (Central region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,1000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.05,
            vjust = 0.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "r1+dcr1_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r1+dcr1_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("r1+dcr1_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r1+dcr1_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to PEA R1 and direct customer in PEA R1 is illustrated in Figure \@ref(fig:EGAT-sale-to-pear1-dcr1-2019). The electricity EGAT sale profiles of PEA R1 and direct customer in PEA R1 are illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R1-2019) and \@ref(fig:EGAT-sale-to-DCR1-2019), respectively.

```{r, EGAT-sale-to-pear1-dcr1-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA R1 and direct customer in PEA R1 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 PEA R2 & DC R2 (North Eastern region) EGAT electrity sale profiles

```{r profile_pear2&dcr2_egtsle2019}
# Profile data ####
profile <-

profiledata$pea_r2_northeastern_egtsle_2019%>%
  mutate(dc_r2 = profiledata$dc_r2_northeastern_egtsle_2019$DCs_R2,
         r2_egt_sle = PEA_R2 + dc_r2) %>% 
  select(-PEA_R2, -dc_r2)

```

```{r, profile-egat-to-pear2-dcr2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R2 and direct customer in PEA R2 profile',
  booktabs = TRUE
)
```

```{r summary_pear2&dcr2_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$r2_egt_sle)) # Get a peak MW
minv <- floor(min(profile$r2_egt_sle)) # Get a min MW
energy <- sum(profile$r2_egt_sle)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r2_egt_sle == max(r2_egt_sle)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r2_egt_sle == min(r2_egt_sle)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egat-to-pear2-dcr2-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R2 and direct customer in PEA R2 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear2&dcr2_egtsle2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r2_egt_sle,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R2 & direct customers (Northern Eastern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,1000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.05,
            vjust = 0.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "r2+dcr2_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r2+dcr2_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("r2+dcr2_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r2+dcr2_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to PEA R2 and direct customer in PEA R2 is illustrated in Figure \@ref(fig:EGAT-sale-to-pear2-dcr2-2019). The electricity EGAT sale profiles of PEA R2 and direct customer in PEA R2 are illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R2-2019) and \@ref(fig:EGAT-sale-to-DCR2-2019), respectively.

```{r, EGAT-sale-to-pear2-dcr2-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA R2 and direct customer in PEA R2 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 PEA R3 & DC R3 (Southern region) EGAT electrity sale profiles

```{r profile_pear3&dcr3_egtsle2019}
profile <-
  
  profiledata$pea_r3_southern_egtsle_2019%>%
  mutate(dc_r3 = profiledata$dc_r3_southern_egtsle_2019$DCs_R3,
         r3_egt_sle = PEA_R3 + dc_r3) %>% 
  select(-PEA_R3, -dc_r3)

```

```{r, profile-egat-to-pear3-dcr3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R3 and direct customer in PEA R3 profile',
  booktabs = TRUE
)
```

```{r summary_pear3&dcr3_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$r3_egt_sle)) # Get a peak MW
minv <- floor(min(profile$r3_egt_sle)) # Get a min MW
energy <- sum(profile$r3_egt_sle)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r3_egt_sle == max(r3_egt_sle)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r3_egt_sle == min(r3_egt_sle)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egat-to-pear3-dcr3-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R3 and direct customer in PEA R3 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear3&dcr3_egtsle2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r3_egt_sle,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R3 & direct customers (Southern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3),1000),
                     limits = c(0, round(maxv, -3))) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.05,
            vjust = 0.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "r3+dcr3_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r3+dcr3_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("r3+dcr3_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r3+dcr3_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to PEA R3 and direct customer in PEA R3 is illustrated in Figure \@ref(fig:EGAT-sale-to-pear3-dcr3-2019). The electricity EGAT sale profiles of PEA R3 and direct customer in PEA R3 are illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R3-2019) and \@ref(fig:EGAT-sale-to-DCR3-2019), respectively.

```{r, EGAT-sale-to-pear3-dcr3-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA R3 and direct customer in PEA R3 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 PEA R4 & DC R4 (Southern region) EGAT electrity sale profiles

```{r profile_pear4&dcr4_egtsle2019}
profile <-
  
  profiledata$pea_r4_northern_egtsle_2019%>%
  mutate(dc_r4 = profiledata$dc_r4_northern_egtsle_2019$DCs_R4,
         r4_egt_sle = PEA_R4 + dc_r4) %>% 
  select(-PEA_R4, -dc_r4)
```

```{r, profile-egat-to-pear4-dcr4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 EGAT sale to PEA R4 and direct customer in PEA R4 profile',
  booktabs = TRUE
)
```

```{r summary_pear4&dcr4_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$r4_egt_sle)) # Get a peak MW
minv <- floor(min(profile$r4_egt_sle)) # Get a min MW
energy <- sum(profile$r4_egt_sle)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r4_egt_sle == max(r4_egt_sle)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r4_egt_sle == min(r4_egt_sle)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egat-to-pear4-dcr4-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale to PEA R4 and direct customer in PEA R4 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear4&dcr4_egtsle2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r4_egt_sle,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale to PEA R4 & direct customers (Northern region) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.2,1000),
                     limits = c(0, round(maxv, -3)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r4+dcr4_egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r4+dcr4_egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("r4+dcr4_egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r4+dcr4_egtsle_2019" = summary))

```

The 2019 electricity sale profile from EGAT to PEA R4 and direct customer in PEA R4 is illustrated in Figure \@ref(fig:EGAT-sale-to-pear4-dcr4-2019). The electricity EGAT sale profiles of PEA R4 and direct customer in PEA R4 are illustrated in Figure \@ref(fig:EGAT-sale-to-PEA-R4-2019) and \@ref(fig:EGAT-sale-to-DCR4-2019), respectively.

```{r, EGAT-sale-to-pear4-dcr4-2019, echo=FALSE,fig.cap='EGAT electricity sale profile to PEA R4 and direct customer in PEA R4 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 EGAT electrity sale profiles
This section provides a combined EGAT electricity sale profile. The equation is given in equation \@ref(eq:prfEgtsleCal)

\begin{equation}
 Prf_{EGTSLE,t,h}=\ Prf_{MEA,t,h} + \sum_{i=1}^{4} (Prf_{PEA,i,t,h} + Prf_{DC,i,t,h}) 
 (\#eq:prfEgtsleCal)
\end{equation} 

Where, 
$Prf_{EGTSLE,t,h}$ denotes the electricity EGAT sale ($EGTSLE$) profile ($Prf$) in year $t$ at time stamp $h$ (MW).\
$Prf_{MEA,t,h}$ denotes the electricity EGAT sale profile ($Prf$) to $MEA$ in year $t$ at time stamp $h$ (MW).\
$Prf_{PEA,i,t,h}$ denotes the electricity EGAT sale profile ($Prf$) to $PEA$ in region $i$ in year $t$ at time stamp $h$ (MW).\
$Prf_{DC,i,t,h}$ denotes the electricity EGAT sale profile ($Prf$) to direct customer ($DC$) in region $i$ in year $t$ at time stamp $h$ (MW).

```{r egtsale_combined_2019}
profile <-
  
  profiledata$mea_egtsle_2019%>%
  mutate(r1_dc1 = profiledata$"r1+dcr1_egtsle_2019"$r1_egt_sle,
         r2_dc2 = profiledata$"r2+dcr2_egtsle_2019"$r2_egt_sle,
         r3_dc3 = profiledata$"r3+dcr3_egtsle_2019"$r3_egt_sle,
         r4_dc4 = profiledata$"r4+dcr4_egtsle_2019"$r4_egt_sle,
         egt_sle = MEA + r1_dc1 + r2_dc2 + r3_dc3 + r4_dc4)
          
```

```{r, profile-egtsale-combined-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  head(profile,5), caption = 'The 2019 electricity EGAT sale profile',
  booktabs = TRUE
)
```

```{r summary_egtsle2019, echo=TRUE, tidy=FALSE}
# Summary data ####
maxv <- ceiling(max(profile$egt_sle)) # Get a peak MW
minv <- floor(min(profile$egt_sle)) # Get a min MW
energy <- sum(profile$egt_sle)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(egt_sle == max(egt_sle)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(egt_sle == min(egt_sle)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egatsale-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of EGAT sale in 2019',
  booktabs = TRUE
)
```

```{r plot_egtsle2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = egt_sle,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT sale (MEA&PEA&DCs) (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,2000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "egtsle_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("egtsle_2019" = profile))
profilefigure <- c(profilefigure, list("egtsle_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_egtsle_2019" = summary))

```


The 2019 electricity EGAT sale profile is illustrated in Figure \@ref(fig:EGAT-sale-2019).

```{r, EGAT-sale-2019, echo=FALSE,fig.cap='EGAT electricity sale profile 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```
