## The electrity requirement profiles
### The 2019 MEA requirement profile
```{r, mea_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = `Date/Time`, MAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, MAC)
  
# Summary data ####
maxv <- ceiling(max(profile$MAC)) # Get a peak MW
minv <- floor(min(profile$MAC)) # Get a min MW
energy <- sum(profile$MAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(MAC == max(MAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(MAC == min(MAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor)
```

```{r, sum-meareq-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a MEA requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_meareq2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = MAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "MEA Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,2000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "mea_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("mea_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("mea_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_mea_requirement_2019" = summary))

```

The 2019 MEA requirement profile is illustrated in Figure \@ref(fig:MEA-REQ-2019).

```{r, MEA-REQ-2019, echo=FALSE,fig.cap='MEA electricity requirment profile in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```


###The 2019 R1 (Central region) requirement for EGAT NET electricity generation profile 

```{r pear1_req_2019}

profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = `Date/Time`, CAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, CAC)

# Summary data ####
maxv <- ceiling(max(profile$CAC)) # Get a peak MW
minv <- floor(min(profile$CAC)) # Get a min MW
energy <- sum(profile$CAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(CAC == max(CAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(CAC == min(CAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear1req-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a PEA R1 requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_pear1req2019}
# Plot a profile ####

profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = CAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "PEA R1 (Central region) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,2000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r1_central_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r1_central_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r1_central_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r1_central_requirement_2019" = summary))

```

The 2019 PEA R1 requirement profile is illustrated in Figure \@ref(fig:PEAR1-REQ-2019).

```{r, PEAR1-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R1 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 R2 (North eastern region) requirement
```{r pear2_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = `Date/Time`, NEC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, NEC)

# Summary data ####
maxv <- ceiling(max(profile$NEC)) # Get a peak MW
minv <- floor(min(profile$NEC)) # Get a min MW
energy <- sum(profile$NEC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(NEC == max(NEC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(NEC == min(NEC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear2req-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a PEA R2 requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_pear2req2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = NEC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "PEA R2 (North Eastern region) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,1000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.1),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r2_northeastern_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r2_northeastern_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r2_northeastern_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r2_northeastern_requirement_2019" = summary))

```

The 2019 PEA R2 requirement profile is illustrated in Figure \@ref(fig:PEAR2-REQ-2019).

```{r, PEAR2-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R2 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 R3 (Southern region) requirement
```{r pear3_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = `Date/Time`, SAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, SAC)

# Summary data ####
maxv <- ceiling(max(profile$SAC)) # Get a peak MW
minv <- floor(min(profile$SAC)) # Get a min MW
energy <- sum(profile$SAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(SAC == max(SAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(SAC == min(SAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear3req-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a PEA R3 requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_pear3req2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = SAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "PEA R3 (Southern region) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,1000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.4),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.1,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r3_southern_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r3_southern_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r3_southern_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r3_southern_requirement_2019" = summary))

```

The 2019 PEA R3 requirement profile is illustrated in Figure \@ref(fig:PEAR3-REQ-2019).

```{r, PEAR3-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R3 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 R4 (Northern region) requirement
```{r pear4_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = `Date/Time`, NAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, NAC)

# Summary data ####
maxv <- ceiling(max(profile$NAC)) # Get a peak MW
minv <- floor(min(profile$NAC)) # Get a min MW
energy <- sum(profile$NAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(NAC == max(NAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(NAC == min(NAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear4req-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a PEA R4 requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_pear4req2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = NAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "PEA R4 (Northern region) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.4,1000),
                     limits = c(0, round(maxv, -3)*1.4)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*1.4),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = 2.5)

# Save the output ####
outputfigure <- paste0(outfigdir, "r4_northern_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r4_northern_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r4_northern_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r4_northern_requirement_2019" = summary))

```

The 2019 PEA R4 requirement profile is illustrated in Figure \@ref(fig:PEAR4-REQ-2019).

```{r, PEAR4-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R4 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 Export TNB (Export to Malaysia) requirement

```{r tnb_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = "Date/Time", export_tnb = "Export TNB") %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, export_tnb)

# Summary data ####
maxv <- ceiling(max(profile$export_tnb)) # Get a peak MW
minv <- floor(min(profile$export_tnb)) # Get a min MW
energy <- sum(profile$export_tnb)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(export_tnb == max(export_tnb)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(export_tnb == min(export_tnb)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-tnbreq-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a TNB requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_tnbreq2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = export_tnb,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "Export to TNB (Malaysia) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-1)*1.2,50),
                     limits = c(0, round(maxv, -1)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -1)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -1)*1.2),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "export_TNB_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("export_TNB_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("export_TNB_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_export_TNB_requirement_2019" = summary))
```

The 2019 TNB requirement profile is illustrated in Figure \@ref(fig:TNB-REQ-2019).

```{r, TNB-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from TNB in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 Export EDL (Export to Cambodia) requirement

```{r edl_req_2019}
profile <-
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "AG3:AN17523"
  ) %>% 
  select(datetime = "Date/Time", export_edl = "Export EDL") %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, export_edl)

# Summary data ####
maxv <- ceiling(max(profile$export_edl)) # Get a peak MW
minv <- floor(min(profile$export_edl)) # Get a min MW
energy <- sum(profile$export_edl)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(export_edl == max(export_edl)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(export_edl == min(export_edl)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-edlreq-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a EDL requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_edlreq2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = export_edl,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "Export to EDL (Laos) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-1)*1.2,50),
                     limits = c(0, round(maxv, -1)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -1)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -1)*1.2),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "export_EDL_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("export_EDL_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("export_EDL_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_export_EDL_requirement_2019" = summary))

```

The 2019 EDL requirement profile is illustrated in Figure \@ref(fig:EDL-REQ-2019).

```{r, EDL-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from EDL in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 R2 + Export EDL (North Eastern + Export to Cambodia) requirement

```{r r2edl_req_2019}
profile <-
  
  profiledata$r2_northeastern_requirement_2019 %>%
  mutate(export_edl = profiledata$export_EDL_requirement_2019$export_edl,
         r2_edl = NEC + export_edl) %>% 
  select(-NEC, -export_edl)

# Summary data ####
maxv <- ceiling(max(profile$r2_edl)) # Get a peak MW
minv <- floor(min(profile$r2_edl)) # Get a min MW
energy <- sum(profile$r2_edl)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r2_edl == max(r2_edl)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r2_edl == min(r2_edl)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-r2edlreq-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a R2 and EDL requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_r2edlreq2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r2_edl,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R2 & Export to EDL (Laos) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.3,1000),
                     limits = c(0, round(maxv, -3)*1.3)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "r2&export_EDL_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r2&export_EDL_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r2&export_EDL_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r2&export_EDL_requirement_2019" = summary))

```

The 2019 R2 and EDL requirement profile is illustrated in Figure \@ref(fig:R2EDL-REQ-2019).

```{r, R2EDL-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R2 and EDL in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 R3 + Export TNB (Southern + Export to Malaysia) requirement

```{r r3tnb_req_2019}
profile <-
  
  profiledata$r3_southern_requirement_2019 %>%
  mutate(export_tnb = profiledata$export_TNB_requirement_2019$export_tnb,
         r3_tnb = SAC + export_tnb) %>% 
  select(-SAC, -export_tnb)

# Summary data ####
maxv <- ceiling(max(profile$r3_tnb)) # Get a peak MW
minv <- floor(min(profile$r3_tnb)) # Get a min MW
energy <- sum(profile$r3_tnb)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(r3_tnb == max(r3_tnb)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(r3_tnb == min(r3_tnb)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-r3tnbreq-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a R3 and TNB requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_r3tnbreq2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = r3_tnb,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R3 & Export to TNB (Malaysia) Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.4,1000),
                     limits = c(0, round(maxv, -3)*1.4)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "r3&export_TNB_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r3&export_TNB_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("r3&export_TNB_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r3&export_TNB_requirement_2019" = summary))

```

The 2019 R3 and TNB requirement profile is illustrated in Figure \@ref(fig:R3TNB-REQ-2019).

```{r, R3TNB-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from PEA R3 and TNB in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

### The 2019 MEA + R1 (MEA + CAC) requirement

```{r mear1_req_2019}
profile <-
  
  profiledata$mea_requirement_2019 %>%
  mutate(r1_requirement = profiledata$r1_central_requirement_2019$CAC,
         mea_r1 = MAC + r1_requirement) %>% 
  select(-MAC, -r1_requirement)

# Summary data ####
maxv <- ceiling(max(profile$mea_r1)) # Get a peak MW
minv <- floor(min(profile$mea_r1)) # Get a min MW
energy <- sum(profile$mea_r1)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(mea_r1 == max(mea_r1)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(mea_r1 == min(mea_r1)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-mear1req-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a MEA and PEA R1 requirement in 2019',
  booktabs = TRUE
)
```

```{r plot_meapear1req2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = mea_r1,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "MEA & R1 Electricity requirement (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.4,1000),
                     limits = c(0, round(maxv, -3)*1.4)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.1),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "mea&r1_requirement_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("mea&r1_requirement_2019" = profile))
profilefigure <- c(profilefigure, list("mea&r1_requirement_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_mea&r1_requirement_2019" = summary))

```

The 2019 MEA and PEA R1 requirement profile is illustrated in Figure \@ref(fig:MEAPEAR1-REQ-2019).

```{r, MEAPEAR1-REQ-2019, echo=FALSE,fig.cap='The electricity requirment profile from MEA and PEA R1 in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 EGAT NET electricity generation profile



```{r egt_ngn_2019}
profile <-
  
  profiledata$`mea&r1_requirement_2019` %>%
  mutate(r2_edl = profiledata$`r2&export_EDL_requirement_2019`$r2_edl,
         r3_tnb = profiledata$`r3&export_TNB_requirement_2019`$r3_tnb,
         r4_requirement = profiledata$r4_northern_requirement_2019$NAC,
         egt_netgen = mea_r1 + r2_edl + r3_tnb + r4_requirement) %>% 
  select(-mea_r1, -r2_edl, -r3_tnb, -r4_requirement)

# Summary data ####
maxv <- ceiling(max(profile$egt_netgen)) # Get a peak MW
minv <- floor(min(profile$egt_netgen)) # Get a min MW
energy <- sum(profile$egt_netgen)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(egt_netgen == max(egt_netgen)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(egt_netgen == min(egt_netgen)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-egtngn-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a EGAT net generation profile in 2019',
  booktabs = TRUE
)
```

```{r plot_egtngn2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = egt_netgen,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "EGAT NET Electricity generation (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-3)*1.1,2000),
                     limits = c(0, round(maxv, -3)*1.1)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -3)*1.05),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            hjust = 0.5) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "egt_netgen_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("egt_netgen_2019" = profile))
profilefigure <- c(profilefigure, list("egt_netgen_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_egt_netgen_2019" = summary))
```

The 2019 EGAT net genration profile is illustrated in Figure \@ref(fig:EGT-NGN-2019).

```{r, EGT-NGN-2019, echo=FALSE,fig.cap='The EGAT net generation profile in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```
