# Total net generation requirement profile

Total net electricity net generation requirement is calculated by the summation of an electricity requirement and VSPP in each region as given in equation \@ref(eq:totalNetGenCal). 


\begin{equation}

TOTNETGEN_{i,t,h} = MEAReq_{t,h} + \sum_{i=1}^{4}(PEAReq_{i,t,h} + VSPP_{i,t,h})
(\#eq:totalNetGenCal)

\end{equation}

Where,
$TOT_NET_GEN_{i,t,h}$ denotes total net electricity generation requirement in region $i$ in year $t$ at time stamp $h$ (MW).\
$MEAReq_{t,h}$ denotes the MEA requirement profile in year $t$ at time stamp $h$ (MW).\
$PEAReq_{i,t,h}$ denotes the PEA requirement profile in region $i$ in year $t$ at time stamp $h$ (MW).\
$VSPP_{i,t,h}$ denotes the electricity generation from $VSPP$ in region $i$ in year $t$ at time stamp $h$ (MW).\

## The 2019 MEA Total net generation requirement profile

```{r meatotnetgen_2019}
profile <-
  
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "BK3:BQ17523") %>% 
  select(datetime = `Date/Time`, MAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, MAC)

# Summary data ####
maxv <- ceiling(max(profile$MAC)) # Get a peak MW
minv <- floor(min(profile$MAC)) # Get a min MW
energy <- sum(profile$MAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(MAC == max(MAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(MAC == min(MAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r, sum-meatotnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of a MEA total net electricity generation profile in 2019',
  booktabs = TRUE
)
```

```{r plot_meatotnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = MAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "MEA Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,1000),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 3) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "mea_total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("mea_total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("mea_total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_mea_total_netgen_req_2019" = summary))

```

The 2019 MEA total net electricity generation is illustrated in Figure \@ref(fig:MEA-TOTNETGEN-2019).

```{r, MEA-TOTNETGEN-2019, echo=FALSE,fig.cap='The MEA total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 PEA R1 (Central region) total net generation requirement profile

```{r pear1totnetgen_2019}
profile <-
  
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "BK3:BQ17523") %>% 
  select(datetime = `Date/Time`, CAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, CAC)

# Summary data ####
maxv <- ceiling(max(profile$CAC)) # Get a peak MW
minv <- floor(min(profile$CAC)) # Get a min MW
energy <- sum(profile$CAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(CAC == max(CAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(CAC == min(CAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear1totnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of total net electricity generation profile in PEA R1 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear1totnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = CAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R1 (Central region) Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,1000),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 1) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = 0)

# Save the output ####
outputfigure <- paste0(outfigdir, "r1_total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r1_total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("r1_total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r1_total_netgen_req_2019" = summary))
```

The 2019 total net electricity generation in PEA R1 is illustrated in Figure \@ref(fig:PEAR1-TOTNETGEN-2019).

```{r, PEAR1-TOTNETGEN-2019, echo=FALSE,fig.cap='The PEA R1 total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 PEA R2 (North Eastern region) total net generation requirement profile

```{r pear2totnetgen_2019}
profile <-
  
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "BK3:BQ17523") %>% 
  select(datetime = `Date/Time`, NEC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, NEC)

# Summary data ####
maxv <- ceiling(max(profile$NEC)) # Get a peak MW
minv <- floor(min(profile$NEC)) # Get a min MW
energy <- sum(profile$NEC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(NEC == max(NEC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(NEC == min(NEC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-pear2totnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of total net electricity generation profile in PEA R2 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear2totnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = NEC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R2 (North Eastern region) Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,1000),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 1) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.05,
            vjust = -1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r2_total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r2_total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("r2_total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r2_total_netgen_req_2019" = summary))
```

The 2019 total net electricity generation in PEA R2 is illustrated in Figure \@ref(fig:PEAR2-TOTNETGEN-2019).

```{r, PEAR2-TOTNETGEN-2019, echo=FALSE,fig.cap='The PEA R2 total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 PEA R3 (Southern region) total net generation requirement profile

```{r pear3totnetgen_2019}
profile <-
  
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "BK3:BQ17523") %>% 
  select(datetime = `Date/Time`, SAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, SAC)

# Summary data ####
maxv <- ceiling(max(profile$SAC)) # Get a peak MW
minv <- floor(min(profile$SAC)) # Get a min MW
energy <- sum(profile$SAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(SAC == max(SAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(SAC == min(SAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r, sum-pear3totnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of total net electricity generation profile in PEA R3 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear3totnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = SAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R3 (Southern region) Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,500),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 1) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = -0.05,
            vjust = -1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r3_total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r3_total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("r3_total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r3_total_netgen_req_2019" = summary))
```

The 2019 total net electricity generation in PEA R3 is illustrated in Figure \@ref(fig:PEAR3-TOTNETGEN-2019).

```{r, PEAR3-TOTNETGEN-2019, echo=FALSE,fig.cap='The PEA R3 total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 PEA R4 (Northern region) total net generation requirement profile

```{r pear4totnetgen_2019}
profile <-
  
  read_excel("raw_data/raw_data_profiles/02_Hourly Sale_NetGen_2019.xlsx",
             sheet = "Load Curve",
             range = "BK3:BQ17523") %>% 
  select(datetime = `Date/Time`, NAC) %>% 
  mutate(date = date(datetime),
         time = format(as.POSIXct(datetime),"%H:%M:%S"),
         year = year(datetime),
         month = month(datetime),
         day = day(datetime)) %>% 
  select(datetime, date, time, year, month, day, NAC)

# Summary data ####
maxv <- ceiling(max(profile$NAC)) # Get a peak MW
minv <- floor(min(profile$NAC)) # Get a min MW
energy <- sum(profile$NAC)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(NAC == max(NAC)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(NAC == min(NAC)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table
```

```{r, sum-pear4totnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of total net electricity generation profile in PEA R4 in 2019',
  booktabs = TRUE
)
```

```{r plot_pear4totnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = NAC,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "R4 (Northern region) Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,500),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 1) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 1,
            vjust = -1)

# Save the output ####
outputfigure <- paste0(outfigdir, "r4_total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("r4_total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("r4_total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_r4_total_netgen_req_2019" = summary))
```

The 2019 total net electricity generation in PEA R4 is illustrated in Figure \@ref(fig:PEAR4-TOTNETGEN-2019).

```{r, PEAR4-TOTNETGEN-2019, echo=FALSE,fig.cap='The PEA R4 total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```

## The 2019 Total net generation requirement profile

Total net electricity generation is calculated by the summation of total net electricity generation in MEA and PEA regions as given in equation \@ref(eq:totalNetGenCal).

```{r totnetgen_2019}
profile <-
  
  profiledata$mea_total_netgen_req_2019 %>% 
  mutate(cac_tot_netgen = profiledata$r1_total_netgen_req_2019$CAC,
         nec_tot_netgen = profiledata$r2_total_netgen_req_2019$NEC,
         sac_tot_netgen = profiledata$r3_total_netgen_req_2019$SAC,
         nac_tot_netgen = profiledata$r4_total_netgen_req_2019$NAC,
         tot_netgen_req = MAC + cac_tot_netgen + nec_tot_netgen + sac_tot_netgen + nac_tot_netgen) %>% 
  select(-MAC, -cac_tot_netgen, -nec_tot_netgen, -sac_tot_netgen, -nac_tot_netgen)

# Summary data ####
maxv <- ceiling(max(profile$tot_netgen_req)) # Get a peak MW
minv <- floor(min(profile$tot_netgen_req)) # Get a min MW
energy <- sum(profile$tot_netgen_req)/2000 # Calculate the energy
peak_day <- profile %>% #Find a peak day
  group_by(year) %>% 
  filter(tot_netgen_req == max(tot_netgen_req)) %>% 
  pull(datetime)
min_day <- profile %>% #Find a min day
  group_by(year) %>% 
  filter(tot_netgen_req == min(tot_netgen_req)) %>% 
  last() %>%  
  pull(datetime)
load_factor <- percent((energy*10^3)/(maxv*8760), 
                       accuracy = 0.01, 
                       decimal.mark = ".")
summary <- tibble(peak_day = peak_day,
                  min_day = min_day,
                  peak_mw = maxv, 
                  min_mw = minv, 
                  energy_gwh = energy,
                  load_factor = load_factor) # combine all data in 1 table

```

```{r, sum-totnetgen-2019, echo=FALSE, tidy=FALSE}
knitr::kable(
  summary, caption = 'Summary of total net electricity generation profile in 2019',
  booktabs = TRUE
)
```

```{r plot_totnetgen2019}
profile_plot <-
  ggplot() + 
  geom_line(data=profile, 
            aes(x = datetime, 
                y = tot_netgen_req,
                group = month,
                color = as.factor(month)),
            show.legend = FALSE) +
  ThemeLine +
  labs(x = NULL,
       y = "Total net generation requiremnet (MW)")+
  scale_x_datetime(breaks=date_breaks("1 month"), 
                   labels=date_format("%b %y")) +
  scale_y_continuous(breaks = seq(0, round(maxv,-2)*1.2,2000),
                     limits = c(0, round(maxv, -2)*1.2)) +  
  scale_color_manual(values = linepalette1) +
  geom_point(data=summary,
             aes(x = peak_day, y = peak_mw))+
  # geom_hline(yintercept = 0) +
  geom_text(data = summary,
            aes(x = peak_day, y = round(maxv, -2)*1.2),
            label = glue("Peak {maxv} MW \n@ {peak_day}"),
            # hjust = 1,
            vjust = 1) +
  geom_point(data=summary,
             aes(x = min_day, y = min_mw))+
  geom_text(data = summary,
            aes(x = min_day, y = round(minv, -3)*0.8),
            label = glue("Minimum {minv} MW \n@ {min_day}"),
            hjust = 0,
            vjust = 1)

# Save the output ####
outputfigure <- paste0(outfigdir, "total_netgen_req_2019.png")
ggsave(profile_plot, file = outputfigure, dpi = 150, width = 15, height = 5, units = "in", limitsize = FALSE)
profiledata <- c(profiledata, list("total_netgen_req_2019" = profile))
profilefigure <- c(profilefigure, list("total_netgen_req_2019" = profile_plot))
summarydata <- c(summarydata, list("sum_total_netgen_req_2019" = summary))
```

The 2019 total net electricity generation is illustrated in Figure \@ref(fig:TOTNETGEN-2019).

```{r, TOTNETGEN-2019, echo=FALSE,fig.cap='Total net electricity generation requirement in 2019.', fig.align='center', out.width= '100%'}
ggplotly(profile_plot) %>% layout(showlegend = FALSE)
```