# EGAT internal electricity use and pump and storage

EGAT internal electricity use is categorized into 2 groups as follows:

* EGAT head office and others
* EGAT substations and their offices
* EGAT station services (other processes in force outage power plants)
* Mae Moh mining
* EGAT pump and storage system

The EGAT electricity consumption data is obtained from Power System Control and Operation Division (ฝ่ายควบคุมระบบกำลังไฟฟ้า (อคฟ.)),
Power Generation and Purchase Data Processing Department (กองประมวลผลข้อมูลการผลิตและซื้อขายไฟฟ้า (กผฟ-ส.)) website.


## Electricity use in office and others

Electricity consumption is taken from Head of National Load forecast section. The file name is `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chunk is given below.


```{r use_office, echo=TRUE, warning=FALSE, message=FALSE}
use_office <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C18:D45",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```


```{r anno_useoffice, echo=FALSE, message=FALSE, warning=FALSE}
annouseoffice2010 <-
    use_office %>% 
    filter(year == 2010) %>% 
    select(-year_th)

annouseoffice2019 <-
    use_office %>% 
    filter(year == 2019)

annouseoffice2023 <-
    use_office %>% 
    filter(year == 2023)
    
```
Electricity use in office and others reached its peak 37 GWh in 2019. In 2023, it assumed that the electricity consumption will be similar to 2018 at 35 GWh according to EGAT staff returned to work onsite (see Figure \@ref(fig:plot-useandoffice)).  

```{r plot-useandoffice, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Electricity consumption in EGAT head office and others', fig.align='center', out.width= '90%'}
use_office %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 50),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 50),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020,2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,50,10),
                     limits = c(0,50))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annouseoffice2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 4,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseoffice2019,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2019$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_y = 4,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseoffice2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 4,
                  inherit.aes = FALSE)
```


## Electricity use in EGAT substations and their office

The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.

```{r use_egatsub, echo=TRUE, warning=FALSE, message=FALSE}
use_egatsub <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C59:D86",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

```{r anno_egatsub, echo=FALSE, warning=FALSE, message=FALSE}
annouseegatsub2010 <-
  use_egatsub %>% 
  filter(year ==2010)

annouseegatsub2015 <-
  use_egatsub %>% 
  filter(year ==2015)

annouseegatsub2023 <-
  use_egatsub %>% 
  filter(year ==2023)
```

Electricity consumption in EGAT substations decreased from 84 GWh in 2010 to 64 GWh in 2015. It is assumed that the electricity consumtion will be similar to those in 2019 (see Figure \@ref(fig:plot-useegatsub)).

```{r plot-useegatsub, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Electricity consumption in EGAT substations', fig.align='center', out.width= '90%'}
use_egatsub %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,150,50),
                     limits = c(0,150))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annouseegatsub2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 10,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseegatsub2015,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2015$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = -10,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseegatsub2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 10,
                  inherit.aes = FALSE)
```

## Electricity use in station service (off-load)

The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.

```{r use_statserv, echo=TRUE, warning=FALSE, message=FALSE}
use_statserv <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C100:D127",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```
```{r anno_use_statserv, echo=FALSE, message=FALSE, warning=FALSE}
annousestatserv2022 <-
  use_statserv %>% 
  filter(year == 2022)

annousestatserv2023 <-
  use_statserv %>% 
  filter(year == 2023)

```


Electricity consumption in station services (off-load) reached its peak 103 GWh in 2022. It is assumed that the consumption in2023 would be similar to those in 2019 (see Figure \@ref(fig:plot-usestatserv)).

```{r plot-usestatserv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Electricity consumption in station service (off-load)', , fig.align='center', out.width= '90%'}
use_statserv %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Data unavailable",
            aes(x = 2011, y = 1),
            size = 3,
            color = "darkgrey",
            nudge_x = 1,
            nudge_y = 10,
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,150,50),
                     limits = c(0,150))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annousestatserv2022,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousestatserv2022$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = 10,
                  inherit.aes = FALSE)+
   geom_text_repel(data = annousestatserv2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousestatserv2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 10,
                  inherit.aes = FALSE)
```



## Electricity use in Mae Moh
The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.
```{r use_maemoh, echo=TRUE, warning=FALSE, message=FALSE}
use_maemoh <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C149:D176",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

## Electricity use in pump and storage
The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.
```{r use_pump, echo=TRUE, warning=FALSE, message=FALSE}
use_pump <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C190:D217",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

## Total electricity consumption

```{r total_usepump, echo=TRUE, warning=FALSE, message=FALSE}
total_usepump <- 
  
  use_office %>% 
  mutate(use_egatsub  = use_egatsub$ely_gwh,
         use_statserv = use_statserv$ely_gwh,
         use_maemoh   = use_maemoh$ely_gwh,
         use_pump     = use_pump$ely_gwh,
         total_usepump  = ely_gwh + use_egatsub + use_statserv + use_maemoh + use_pump)
```

