# EGAT internal electricity use and pump and storage

EGAT internal electricity use is categorized into 5 groups as follows:

* EGAT head office and others
* EGAT substations and their offices
* EGAT station services (other processes in force outage power plants)
* Mae Moh mining
* EGAT pump and storage system

The EGAT electricity consumption data is obtained from Power System Control and Operation Division (ฝ่ายควบคุมระบบกำลังไฟฟ้า (อคฟ.)),
Power Generation and Purchase Data Processing Department (กองประมวลผลข้อมูลการผลิตและซื้อขายไฟฟ้า (กผฟ-ส.)) [website](http://control.egat.co.th/gpddwebsite/index.aspx).


## Electricity consumption in EGAT head office and others {#elyegatheadoffice}

Electricity consumption is taken from Head of National Load forecast section. The file name is `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chunk is given below.


```{r use_office, echo=TRUE, warning=FALSE, message=FALSE}
use_office <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C18:D45",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```


```{r anno_useoffice, echo=FALSE, message=FALSE, warning=FALSE}
annouseoffice2010 <-
    use_office %>% 
    filter(year == 2010) %>% 
    select(-year_th)

annouseoffice2019 <-
    use_office %>% 
    filter(year == 2019)

annouseoffice2023 <-
    use_office %>% 
    filter(year == 2023)
    
```

An electricity use in EGAT head office and others reached its peak 37 GWh in 2019. In 2023, it assumed that the electricity consumption will be similar to those in 2018 at 35 GWh due to EGAT staff returned to work onsite (see Figure \@ref(fig:plot-useandoffice)).  

```{r plot-useandoffice, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Electricity consumption in EGAT head office and others', fig.align='center', out.width= '90%'}
use_office %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 50),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 50),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020,2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,50,10),
                     limits = c(0,50))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annouseoffice2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 4,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseoffice2019,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2019$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_y = 4,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseoffice2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseoffice2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 4,
                  inherit.aes = FALSE)
```


## Electricity consumption in EGAT substations and their offices {#elyegatsub}

The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.

```{r use_egatsub, echo=TRUE, warning=FALSE, message=FALSE}
use_egatsub <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C59:D86",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

```{r anno_egatsub, echo=FALSE, warning=FALSE, message=FALSE}
annouseegatsub2010 <-
  use_egatsub %>% 
  filter(year ==2010)

annouseegatsub2015 <-
  use_egatsub %>% 
  filter(year ==2015)

annouseegatsub2023 <-
  use_egatsub %>% 
  filter(year ==2023)
```

An electricity consumption in EGAT substations decreased from 84 GWh in 2010 to 64 GWh in 2015. It is assumed that the electricity consumption will be similar to those in 2019 (see Figure \@ref(fig:plot-useegatsub)).

```{r plot-useegatsub, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Electricity consumption in EGAT substations', fig.align='center', out.width= '90%'}
use_egatsub %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,150,50),
                     limits = c(0,150))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annouseegatsub2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 10,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseegatsub2015,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2015$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = -10,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annouseegatsub2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annouseegatsub2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 10,
                  inherit.aes = FALSE)
```

## Electricity consumption in station service (off-load) {#elystationservice}

The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.

```{r use_statserv, echo=TRUE, warning=FALSE, message=FALSE}
use_statserv <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C100:D127",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```
```{r anno_use_statserv, echo=FALSE, message=FALSE, warning=FALSE}
annousestatserv2022 <-
  use_statserv %>% 
  filter(year == 2022)

annousestatserv2023 <-
  use_statserv %>% 
  filter(year == 2023)

```


An electricity consumption in station services (off-load) reached its peak 103 GWh in 2022. It is assumed that the consumption in 2023 would be similar to those in 2019 (see Figure \@ref(fig:plot-usestatserv)).

```{r plot-usestatserv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Electricity consumption in station service (off-load)', fig.align='center', out.width= '90%'}
use_statserv %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Data unavailable",
            aes(x = 2011, y = 1),
            size = 3,
            color = "darkgrey",
            nudge_x = 1,
            nudge_y = 10,
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 150),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,150,50),
                     limits = c(0,150))+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annousestatserv2022,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousestatserv2022$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = 10,
                  inherit.aes = FALSE)+
   geom_text_repel(data = annousestatserv2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousestatserv2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 10,
                  inherit.aes = FALSE)
```


## Electricity consumption in Mae Moh mining {#elymaemoh}
The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.
```{r use_maemoh, echo=TRUE, warning=FALSE, message=FALSE}
use_maemoh <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C149:D176",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

```{r anno_use_maemoh, echo=FALSE, warning=FALSE, message=FALSE}
annousemaemoh2010 <-
  use_maemoh %>% 
  filter(year == 2010)

annousemaemoh2017 <-
  use_maemoh %>% 
  filter(year == 2017)

annousemaemoh2023 <-
  use_maemoh %>% 
  filter(year == 2023)

annousemaemoh2026 <-
  use_maemoh %>% 
  filter(year == 2026)

annousemaemoh2029 <-
  use_maemoh %>% 
  filter(year == 2029)

annousemaemoh2035 <-
  use_maemoh %>% 
  filter(year == 2035)

```

An electricity consumption in Mea Moh mining would reach its peak 912 GWh in 2023 and would gradually decrease (see Figure \@ref(fig:plot-usemaemoh)). A mining electricity consumption depends on a mining schedule. It is unpredictable. It should be closely monitored. The contact number is Tel. **66440** (internal call), Mechanical and Electrical Engineering Department (กวคฟ-ช.), Fuel Engineering Division (อวพ.), Deputy Governor-Fuel (รวช.).   
```{r plot-usemaemoh, echo=FALSE,warning=FALSE, message=FALSE, fig.cap='Electricity consumption in Mae Moh mining', fig.align='center', out.width= '90%'}
use_maemoh %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 1200),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 1200),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,1200,100),
                     limits = c(0,1200),
                     labels = comma)+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annousemaemoh2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = -100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousemaemoh2017,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2017$ely_gwh, format = "d"), " GWh")),
                  size = 4,
                  nudge_y = -100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousemaemoh2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2023$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = 100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousemaemoh2026,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2026$ely_gwh, format = "d"), " GWh")),
                  size = 4,
                  nudge_y = -100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousemaemoh2029,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2029$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = 100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousemaemoh2035,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousemaemoh2035$ely_gwh, format = "d"), " GWh")),
                  # hjust = 0.9,
                  size = 4,
                  # nudge_x = 3.5,
                  nudge_y = -100,
                  inherit.aes = FALSE)
```


## Electricity consumption in pumped storage hydropower plants {#elypump}
The data is extracted from `01 EGAT_20Oct2022_งบ66 67_Final.xlsx`. The R code chuck is given below.
```{r use_pump, echo=TRUE, warning=FALSE, message=FALSE}
use_pump <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C190:D217",
             col_names = c("year_th", "ely_gwh")) %>% 
  mutate(year = year_th - 543)
```

```{r anno_use_pump, echo=FALSE, message=FALSE, warning=FALSE}
annousepump2010 <-
  use_pump %>%
  filter(year == 2010)

annousepump2020 <-
  use_pump %>%
  filter(year == 2020)

annousepump2023 <-
  use_pump %>%
  filter(year == 2023)
```

As of August 2023, there are 3 EGAT's pumped storage hydropower plants as follows:

* **Srinagarind** pumped storage hydropower plant **unit 4 and 5**, Kanchanaburi with **360 MW** of installed capacity;
* **Bhumibol** pumped storage hydropower plant **unit 8**, Tak with **171 MW** of installed capacity; and
* **Lamtakong** pumped storage hydropower plant, Nakorn Ratchasima with **1,000 MW** of installed capacity


The *Chulabhorn* pumped storage hydropower plant is currently under an Environmental Impact Assessment (EIA). The plant's commercial operation date (COD) would be in *2034* with *800 MW* of installed capacity.\


An electricity consumption by pumped storage hydropower plants increased from 434 GWh in 2010 and reached it peak 610 GWh in 2020. Power System Control and Operation Division (ฝ่ายควบคุมระบบกำลังไฟฟ้า (อคฟ.)) estimates a yearly operation short- and a long-term plans. It is estimated that the electricity consumption would be 555 GWh in 2023 until 2037 (see Figure \@ref(fig:plot-usepump)). It accounts only the electricity consumption in the Lamtakong pumped storage hydropower plant.

```{r plot-usepump, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Electricity consumption by pumped storage hydropower plants', fig.align='center', out.width= '90%'}
use_pump %>% 
  ggplot(aes(x = year, y = ely_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 800),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 800),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,800,100),
                     limits = c(0,800),
                     labels = comma)+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annousepump2010,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousepump2010$ely_gwh, format = "d"), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3.5,
                  nudge_y = 50,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousepump2020,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousepump2020$ely_gwh, format = "d"), " GWh")),
                  size = 4,
                  nudge_y = 50,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annousepump2023,
                  aes(x = year, y = ely_gwh,
                      label = paste0(formatC(annousepump2023$ely_gwh, format = "d"), " GWh")),
                  size = 4,
                  nudge_x = 1,
                  nudge_y = 50,
                  inherit.aes = FALSE)
```

## Total EGAT internal electricity consumption

Total EGAT internal electricity consumption can be found in equation \@ref(eq:totalUsePump).

\begin{equation}
\begin{split}

TOTUSEPUMP_{t}  = & ELY_{headoffice,t}+ELY_{substation,t}+ELY_{stationserv,t}+\\
                  & ELY_{maemoh,t}+ELY_{pump,t}
(\#eq:totalUsePump)

\end{split}
\end{equation}

Where,\
$TOTUSEPUMP_{t}$ denotes total EGAT internal electricity consumption in year $t$.\
$ELY_{headoffice}$ denotes an electricity consumption in EGAT head office and others in year $t$ (see section \@ref(elyegatheadoffice)).\
$ELY_{substation}$ denotes an electricity consumption in EGAT substations in year $t$ (see section \@ref(elyegatsub)).\
$ELY_{stationserv,t}$ denotes an electricity consumption in EGAT station services in year $t$ (see section \@ref(elystationservice)).\
$ELY_{maemoh,t}$ denotes an electricity consumption in EGAT Mae Moh mining in year $t$ (see section \@ref(elymaemoh)).\
$ELY_{pump,t}$ denotes an electricity consumption in EGAT pumped storage hydropower plants in year $t$ (see section \@ref(elypump)).\


```{r total_usepump, echo=TRUE, warning=FALSE, message=FALSE}
total_usepump <-
  
  use_office %>% 
  select(year, use_office = ely_gwh) %>% 
  mutate(use_egatsub  = use_egatsub$ely_gwh,
         use_statserv = use_statserv$ely_gwh,
         use_maemoh   = use_maemoh$ely_gwh,
         use_pump     = use_pump$ely_gwh,
         total_usepump  = use_office + use_egatsub + use_statserv + use_maemoh + use_pump)
```

```{r anno_totalusepump, echo=FALSE, message=FALSE, warning=FALSE}
annototalusepump2010 <-
total_usepump %>% 
  select(year, total_usepump) %>% 
  filter(year == 2010)

annototalusepump2021 <-
total_usepump %>% 
  select(year, total_usepump) %>% 
  filter(year == 2021)

annototalusepump2023 <-
total_usepump %>% 
  select(year, total_usepump) %>% 
  filter(year == 2023)

annototalusepump2035 <-
total_usepump %>% 
  select(year, total_usepump) %>% 
  filter(year == 2035)
```

Total EGAT internal electricity consumption increased from 902 GWh in 2010 and will reaches it peak 1,674 GWh in 2023. In 2037, the consumption will decline to 1,259 GWh (see Figure \@ref(fig:plot-totalusepump)). Figure \@ref(fig:plot-facettotalusepump) illustates electricity consumption by category. **Mae Moe mining** plays an key role in using the EGAT internal electricity consumption, followed by **pumped storage hydropower plants**.
```{r plot-totalusepump, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Total EGAT internal electricity consumption', fig.align='center', out.width= '90%'}
total_usepump %>% 
  ggplot(aes(x = year, y = total_usepump)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2022)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_text(label = "Historical data",
            aes(x = 2016, y = 2000),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 2000),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010,2015, 2020, 2025, 2030,2037))+
  scale_y_continuous(breaks = seq(0,2000,200),
                     limits = c(0,2000),
                     labels = comma)+
  ThemeLine+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")+
  geom_text_repel(data = annototalusepump2010,
                  aes(x = year, y = total_usepump,
                      label = paste0(formatC(annototalusepump2010$total_usepump, format = "d"), " GWh")),
                  hjust = 0.5,
                  size = 4,
                  nudge_x = 1.8,
                  nudge_y = 100,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annototalusepump2021,
                  aes(x = year, y = total_usepump,
                      label = paste0(formatC(annototalusepump2021$total_usepump, format = "d", big.mark = ","), " GWh")),
                  hjust = 0.5,
                  size = 4,
                  nudge_x = -1.8,
                  nudge_y = 200,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annototalusepump2023,
                  aes(x = year, y = total_usepump,
                      label = paste0(formatC(annototalusepump2023$total_usepump, format = "d", big.mark = ","), " GWh")),
                  hjust = 0.5,
                  size = 4,
                  nudge_x = 1.8,
                  nudge_y = 200,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annototalusepump2035,
                  aes(x = year, y = total_usepump,
                      label = paste0(formatC(annototalusepump2035$total_usepump, format = "d", big.mark = ","), " GWh")),
                  hjust = 0.5,
                  size = 4,
                  nudge_x = 1.8,
                  nudge_y = 200,
                  inherit.aes = FALSE)
```

```{r plot-facettotalusepump, echo=FALSE, message = FALSE, warning = FALSE, fig.cap = 'Total EGAT electricity consumption by categories', fig.align='center', out.width= '90%'}
use_office %>% 
  select(year, use_office = ely_gwh) %>% 
  mutate(use_egatsub  = use_egatsub$ely_gwh,
         use_statserv = use_statserv$ely_gwh,
         use_maemoh   = use_maemoh$ely_gwh,
         use_pump     = use_pump$ely_gwh,
         total_usepump  = use_office + use_egatsub + use_statserv + use_maemoh + use_pump) %>% 
  pivot_longer(-year, names_to = "use", values_to = 'ely_gwh') %>%
  mutate(use = factor(use,c("use_office", "use_egatsub","use_statserv","use_maemoh","use_pump","total_usepump"))) %>% 
  ggplot(aes(x = year, y = ely_gwh))+
  geom_line(aes(group = use, color = use), show.legend = FALSE)+
  geom_point(shape = 21,
             size = 1,
             color = "black",
             fill = "grey")+
  facet_wrap(~use,
             scales = "free_y",
             labeller = as_labeller(c(use_office = "EGAT head office",
                          use_egatsub = "EGAT substations",
                          use_statserv = "Station services",
                          use_maemoh = "Mae Moh mining",
                          use_pump = "Pumped storage",
                          total_usepump = "TOTAL consumption")))+
  scale_x_continuous(breaks = c(2010, 2015,2020,2025,2030,2037))+
  scale_y_continuous(labels = comma)+
  ThemeLine+
  scale_color_manual(values = linepalette1)+
  labs(x = NULL,
       y = "Electricity consumption (GWh)")
```

