# Transmission loss in EGAT power system

A transmission loss data is obtained from Power System Control and Operation Division (ฝ่ายควบคุมระบบกำลังไฟฟ้า (อคฟ.)),
Power Generation and Purchase Data Processing Department (กองประมวลผลข้อมูลการผลิตและซื้อขายไฟฟ้า (กผฟ-ส.)) [website](http://control.egat.co.th/gpddwebsite/ReportYear_Table_01.aspx) (EGAT intranet only).\

The transmission loss is calculated by an equation \@ref(eq:transloss) as follows:

\begin{equation}


TRNLSS_{t}  = \frac{LSS_{t}}{EGATSLE_{t}}
(\#eq:transloss)


\end{equation}

Where, $TRNLSS_{t}$ denotes a transmission loss in year $t$ in percentage.\
$LSS_{t}$ denotes a transmission loss in year $t$ in GWh.
$EGATSLE_{t}$ denotes a EGAT electricity sale in year $t$ in GWh.

```{r percenttransloss, echo=TRUE, warning=FALSE, message=FALSE}
tran_loss_percent <- 
  
  read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final.xlsx",
             sheet = "C_LossUse",
             range = "C321:D348",
             col_names = c("year_th", "percent_loss")) %>% 
  mutate(year = year_th - 543)
```
```{r anno_transloss, echo=FALSE, warning=FALSE, message=FALSE}

annotransloss2010 <-
tran_loss_percent %>% 
  filter(year == 2010)

annotransloss2021 <-
tran_loss_percent %>% 
  filter(year == 2021)

annotransloss2022 <-
tran_loss_percent %>% 
  filter(year == 2022)
```

The transmission loss decreased from 1.94% in 2010 to 1.57% in 2021. It is assumed that the loss would be similar to those in 2019. The reason is that the EGAT electricity sale in 2020 and 2021 was in a pandemic situation. The transmission loss would be 1.65% from 2022 onwards.

```{r plot-translosspercent, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Transmission loss in EGAT power system', fig.align='center', out.width= '90%'}

tran_loss_percent %>%
  ggplot(aes(x = year, y = percent_loss)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_vline(xintercept = 2010)+
  geom_vline(xintercept = 2021)+
  geom_text(label = "Historical data",
            aes(x = 2015.5, y = 0.03),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 0.03),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2010, 2015,2020,2025,2030,2037))+
  scale_y_continuous(breaks = seq(0,0.03,0.005),
                     limits = c(0,0.03),
                     labels = scales::percent)+
  ThemeLine+
  labs(x = NULL,
       y = "Transmission loss (%)")+
  geom_text_repel(data = annotransloss2010,
                  aes(x = year, y = percent_loss,
                      label = paste0(formatC(annotransloss2010$percent_loss*100, format = "g", digits = 3), " %")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 0.001,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annotransloss2021,
                  aes(x = year, y = percent_loss,
                      label = paste0(formatC(annotransloss2021$percent_loss*100, format = "g", digits = 3), " %")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = -1,
                  nudge_y = 0.003,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annotransloss2022,
                  aes(x = year, y = percent_loss,
                      label = paste0(formatC(annotransloss2022$percent_loss*100, format = "g", digits = 3), " %")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 2,
                  nudge_y = 0.003,
                  inherit.aes = FALSE)
  
```

