# EGAT direct customers

EGAT direct customers are as follows:

* 14 domestic customers
** Sattahip Navy station
** Voice of America (VOA) radio station
** SCG Tung Song
** SCG Ta Luang
** Jalaprathan cement
** Siam Iron and Steel
** Padaeng industry
** ESSO Ao Phai
** IPP-Ratch (Tharab)
** IPP-Ratchburi power
** Others
** IPP & SPP standby
** Temporary
** Thaioil

* 12 neighboring customers
** Electricité du Cambodge (EDC)
** Tenaga Nasional Berhad (TNB)
** Électricité du Laos (EDL)
** Theun Hinboun Hydro Power Plant (เทิน-หินบุน)
** Houay Ho Hydro Power Plant (ห้วยเฮาะ)
** Nam Theun 2 Hydro Power Plant (น้ำเทิน 2)
** Nam Ngum 2 Hydro Power Plant (น้ำงึม 2)
** Hongsa Mine Mouth Thermal Power Plant
** Xe-Pian Xe-Namnoy Hydro Power Plant (เซเปียน-เซน้ำน้อย)
** Nam Ngiep 1 Hydro Power Plant (น้ำเงี๊ยบ 1)
** Xayaburi Hydro Power Plant
** Nam Theun 1 Hydro Power Plant (น้ำเทิน 1)

A historical purchased electricity between 2019–2021, is obtained from a budget load approved on *September 2022*. An estimated electricity purchased electricity is taken from a budget load approved on *March 2022*. The R code chunk are given below. \

The historical and estimated purchased electricity are named as `b_dc_ene` and `pdp2022_dc_ene`, respectively.

```{r dcELYBudgetloadSep2022, echo=TRUE, warning=FALSE, message=FALSE}
b_dc_ene <-
  
read_excel("raw_data/01 EGAT_20Oct2022_งบ66 67_Final_Sent อศง.xlsx",
           sheet = "DCs",
           range = "A6:K44",
           col_names = c("direct_cus", 2019:2028)) %>% 
  drop_na() %>% 
  filter(str_detect(direct_cus, "Energy Demand ")) %>% 
  pivot_longer(-direct_cus, names_to = "year", values_to = "dc_gwh") %>% 
  mutate(year = as.numeric(year),
         year_th = year + 543)

```

```{r dcELYPDP2022Mar2022, echo=TRUE, warning=FALSE, message=FALSE}
pdp2022_dc_ene <-
  
read_excel("raw_data/93 EGAT_25Aug2022_13 Energy ภาพรวม NIDA_BAU_ND_EE70__Sent.xlsx",
           sheet = "DCs_Mar_BAU",
           range = "A6:V51",
           col_names = c("direct_cus", 2017:2037)) %>% 
  drop_na() %>% 
  filter(str_detect(direct_cus, "Energy Demand ")) %>% 
  pivot_longer(-direct_cus, names_to = "year", values_to = "dc_gwh") %>%
  filter(direct_cus == "Energy Demand of  OVER ALL") %>% 
  mutate(year = as.numeric(year),
         year_th = year + 543) %>% 
  filter(year >= 2029)

```

A `rbind` function is a function combined EGAT direct customers. It is named `newdc_ene`.

```{r combineDCELY, echo=FALSE, warning=FALSE, message=FALSE}
newdc_ene <- rbind(x = b_dc_ene, y = pdp2022_dc_ene)
```  
```{r anno_dcELY, echo=FALSE, message=FALSE, warning=FALSE}
annodcely2019 <-
  newdc_ene %>% 
  filter(year == 2019)

annodcely2021 <-
  newdc_ene %>% 
  filter(year == 2021)

annodcely2030 <-
  newdc_ene %>% 
  filter(year == 2030)

annodcely2037 <-
  newdc_ene %>% 
  filter(year == 2037)
```


```{r plot-directCustomer, echo=FALSE, warning=FALSE, message=FALSE, fig.cap='Purchased electricity by EGAT direct customers', fig.align='center', out.width= '90%'}
newdc_ene %>% 
  ggplot(aes(x = year, y = dc_gwh)) +
  geom_line(aes(color = "salmon"),
            show.legend = FALSE)+
  geom_point(shape = 21,
             size = 2,
             color = "salmon",
             fill = "grey")+
  geom_vline(xintercept = 2019)+
  geom_vline(xintercept = 2021)+
  geom_text(label = "Historical data",
            aes(x = 2020, y = 6000),
            color = "dodgerblue",
            size = 2.5,
            show.legend = FALSE,
            inherit.aes = FALSE)+
  geom_text(label = "Projected data",
            aes(x = 2030, y = 6000),
            color = "dodgerblue",
            show.legend = FALSE,
            inherit.aes = FALSE)+
  scale_x_continuous(breaks = c(2019, 2021,2025,2030,2037))+
  scale_y_continuous(breaks = seq(0,6000,500),
                     limits = c(0,6000),
                     labels = scales::comma)+
  ThemeLine+
  labs(x = NULL,
       y = "Purchased electricity (GWh)")+
  geom_text_repel(data = annodcely2019,
                  aes(x = year, y = dc_gwh,
                      label = paste0(formatC(annodcely2019$dc_gwh, format = "d", big.mark = ","), " GWh")),
                  # hjust = 0.9,
                  size = 4,
                  nudge_x = 1,
                  nudge_y = 500,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annodcely2021,
                  aes(x = year, y = dc_gwh,
                      label = paste0(formatC(annodcely2021$dc_gwh, format = "d", big.mark = ","), " GWh")),
                  hjust = 0.9,
                  size = 4,
                  nudge_x = 3,
                  nudge_y = 500,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annodcely2030,
                  aes(x = year, y = dc_gwh,
                      label = paste0(formatC(annodcely2030$dc_gwh, format = "d", big.mark = ","), " GWh")),
                  # hjust = 0.9,
                  size = 4,
                  nudge_x = 1,
                  nudge_y = 500,
                  inherit.aes = FALSE)+
  geom_text_repel(data = annodcely2037,
                  aes(x = year, y = dc_gwh,
                      label = paste0(formatC(annodcely2037$dc_gwh, format = "d", big.mark = ","), " GWh")),
                  # hjust = 0.9,
                  size = 4,
                  nudge_x = -1,
                  nudge_y = 500,
                  inherit.aes = FALSE)

```

